A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-25 paper/paper.tex
paper: equalize columns on last page
paper: fix an underfull hbox

\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, minted, rotating}
\usepackage[prefix=bonak]{art.cls/xkeymask}
\usetikzlibrary{patterns}

@@

The operation $\restrf[n][p][\epsilon][q]$ indicates restriction on $q$ layers of a frame, and the induction is on $p$, going from $0$ to $q$. In particular, $\restrf[n][p][\epsilon][p]$ is a ``full restriction''. We define $\restrf[n][p][\epsilon][p](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\painting$. The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\painting[n][p]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][p][L][p]$ picks out $c_L$, a $\painting[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\painting[n-1][p]$, and $\_$, a $\painting[n][p+1]$, is discarded. There is one more difficulty, which we illustrate by writing down expected and actual types.

>>>>

\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, rotating, flushend}

\makeatletter
\@namedef{ver@lineno.sty}{9999/12/31}
\@namedef{opt@lineno.sty}{}
\makeatother
\usepackage{minted}

\usepackage[prefix=bonak]{art.cls/xkeymask}
\usetikzlibrary{patterns}

@@

The operation $\restrf[n][p][\epsilon][q]$ indicates restriction on $q$ layers of a frame, and the induction is on $p$, from $0$ to $q$. In particular, $\restrf[n][p][\epsilon][p]$ is a ``full restriction''. We define $\restrf[n][p][\epsilon][p](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\painting$. The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\painting[n][p]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][p][L][p]$ picks out $c_L$, a $\painting[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\painting[n-1][p]$, and $\_$, a $\painting[n][p+1]$, is discarded. There is one more difficulty, which we illustrate by writing down expected and actual types.
